Computer Science House Constitution

### 2016-04-21 articles.tex
update articles.tex for clarity
This text better reflects what I intended and makes reading easier.

\asubsection{Semantic Changes}
Any semantic change to the Constitution requires the change to be brought up at House Meeting and proposed in writing for discussion at the following House Meeting.
The text of the change may be modified up until the aforementioned House Meeting. 
At the beginning of the discussion period, ballots are distributed for a balloted House vote as described in \ref{Balloted Vote}.
Attendance for the discussion on the change is not mandatory.
The ballots are collected for a minimum of a forty-eight hour period.
A quorum of two-thirds of the Total Number of Possible Votes must cast ballots for the vote to be official.
A vote equaling or exceeding two-thirds of the number of votes cast is required for the change to be placed into the constitution.
The Constitution may be overridden by an immediate House vote as described in \ref{Immediate Vote}.
There must be a quorum of eighty-five percent of the Total Number of Possible Votes for the vote to be official.
A vote equaling or exceeding ninety percent of the number of votes cast is required for the override to take effect.

>>>>

\asubsection{Semantic Changes}
Any semantic change to the Constitution requires the change to be brought up at House Meeting and proposed in writing for discussion at the following House Meeting.
The text of the change may be modified up until the House Meeting at which it is discussed. 
Before beginning discussion, ballots are distributed for a balloted House vote as described in \ref{Balloted Vote}.
Attendance for the discussion on the change is not mandatory.
The ballots are collected for a minimum of a forty-eight hour period.
A quorum of two-thirds of the Total Number of Possible Votes must cast ballots for the vote to be official.
A vote equaling or exceeding two-thirds of the number of votes cast is required for the change to be placed into the constitution.
The Constitution may be overridden by an immediate House vote as described in \ref{Immediate Vote}.
There must be a quorum of eighty-five percent of the Total Number of Possible Votes for the vote to be official.
A vote equaling or exceeding ninety percent of the number of votes cast is required for the override to take effect.
